---
title: "HM#1 rmarkdown"
output: pdf_document
author: Steven Indrayana Istimur 20554526
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coding Howework (submmited to Canvas )
Use the dataset Demographics_State.csv, and conduct the following data analysis in R.

```{r}
dat <- read.csv(file = 'Demographics_State.csv')
head(dat)
```

(1) Compute the average, median, range, standard deviation and quartiles of total\_population.

```{r ave med range sd quartile}
#input your r code here
ave = mean(dat$total_population)
med = median(dat$total_population)
ran = max(dat$total_population) - min(dat$total_population)
std = sd(dat$total_population)
qrt = quantile(dat$total_population)

cat(" Average \t: ", ave, '\n',
    "Median \t \t: ", med, '\n',
    "Range  \t \t: ", ran, '\n',
    "Standard Deviation \t: ", std, '\n',
    "Quartile (Q1)\t \t: ", qrt[2],'\n',
    "Quartile (Q2)\t \t: ", qrt[3],'\n',
    "Quartile (Q3)\t \t: ", qrt[4])
    
```

(2) Plot the histogram and the boxplot of total\_population.

```{r histogram boxplot}
#input your r code here
hist(dat$total_population, 
     main = "Histogram of Demographics State",
     xlab = "Total Population")

boxplot(dat$total_population,
        main = "Boxplot of Total Population")
```

(3) Draw the scatter plot of total\_population versus median\_age. Compute the covariance of the two variables without and then with the built-in function; check if the results are the same.

```{r covariance}
#input your r code here
#scatter plot
plot(dat$median_age,
     dat$total_population, 
     main = "Scatter Plot of Demographics State",
     xlab = "Median Age", 
     ylab = "Total Population")
```
```{r}
#covariance without built-in function
cov_1 = 0
for (i in c(1:length(dat$total_population))) {
  cov_1 = cov_1 + 
        ((dat$total_population[i] - mean(dat$total_population)) * 
        (dat$median_age[i]- mean(dat$median_age)))
}
cov_1 = cov_1 / (length(dat$total_population)-1)



#covariance built-in function
cov_2 = cov(dat$total_population, dat$median_age)

cat("The Cov(Total Population, Median Age)\n",
    "without built-in function \t:",
    cov_1,
    "\n with built-in function \t \t:",
    cov_2)
```
