---
title: "Homework2"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coding Howework (submmite the pdf file to Canvas)
Let $X$ be a Possion$(\lambda)$ random variable. We have seen in class that $$\mathbb E(X) = \mathrm{Var}(X) = \lambda.$$ Suppose that we do not know the true value of $\lambda$ and want to estimate it from observed data $\{x_1,x_2, \dots, x_n\}$.  There are two possible ways to do estimate $\lambda$:
\begin{itemize}
\item use the sample mean $\bar{x} = \frac{1}{n}\sum_{i = 1}^{n} x_i$
\item use the sample variance $S^2 = \frac{1}{n-1} \sum_{i = 1}^{n} (x_i - \bar{x})^2$
\end{itemize}
**Please note that in sample variance, the denominator is $n-1$ instead of $n$.**

In this assignment, you will compare the two estimators.  **In the following questions, we assume that $\lambda = 10$.**

1. Generate $n = 10$ independent Poisson$(\lambda)$ random variables, calculate the sample mean (you can use \verb+rpois(n = ,lambda = )+ function in \verb+R+, where \verb+n+ is the total number of random varables generated and \verb+\lambda+ is the parameter $\lambda$). Do the above $1000$ times, then you have $1000$ observations of the _sample mean_ (each of them is calculated from $n=10$  independent Poisson $(\lambda)$ random variables.)  **Generate the boxplot and histogram of the $1000$ observation of sample means.**

```{r sample mean}
# input your r code here
x1 <- c()
for (i in 1:1000){
  x1[i] = mean(rpois(n = 10, lambda = 10))
}
hist(x1,
     main = "Histogram of Estimation using Sample Mean",
     xlab = "Lambda Value")

boxplot(x1,
        main = "Boxplot of Estimation using Sample Mean",
        ylab = "Lamda Value" )

```

2. For $n = 10$, **repeat Part 1 with the _sample variance_.**

```{r sample variance}
# input your r code here
x2 <- c()
for (i in 1:1000){
  x2[i] = var(rpois(n = 10, lambda = 10))
}
hist(x2,
     main = "Histogram of Estimation using Sample Variance",
     xlab = "Lambda Value")

boxplot(x2,
        main = "Boxplot of Estimation using Sample Variance",
        ylab = "Lamda Value")
```

3. Compare the boxplot and histogram you obtained from Part 1 and 2.  **Comment on the difference between them.** (Hint: measure of dispersion)

```{r boxplot and histogram}
# input your r code here
med1 = median(x1)
ran1 = max(x1) - min(x1)
std1 = sd(x1)
qrt1 = quantile(x1)

med2 = median(x2)
ran2 = max(x2) - min(x2)
std2 = sd(x2)
qrt2 = quantile(x2)


cat("Sample Mean as the Estimator", '\n',
    "Median \t \t: ", med1, '\n',
    "Range  \t \t: ", ran1, '\n',
    "Standard Deviation \t: ", std1, '\n',
    "Quartile (Q1)\t \t: ", qrt1[2],'\n',
    "Quartile (Q3)\t \t: ", qrt1[4], '\n')

cat("Sample Variance as the Estimator", '\n',
    "Median \t \t: ", med2, '\n',
    "Range  \t \t: ", ran2, '\n',
    "Standard Deviation \t: ", std2, '\n',
    "Quartile (Q1)\t \t: ", qrt2[2],'\n',
    "Quartile (Q3)\t \t: ", qrt2[4])
```

**Write down your comments here**
From the histogram of (1) estimation using ‘sample mean’and (2) estimation using ’sample variance’, we can compare respectively that:

- The shape of the first histogram almost show a perfectly simmetrical distribution, but the second histogram is positively skewed.

- It also can be seen that the first Standard Deviation of the first histogram is a lot smaller than the second histogram.

Meanwhile, from the boxpot of (1) estimation using ‘sample mean’ and (2) estimation using ’sample variance’ we can analyze the 5-Number Summary:

- The Median of the first boxplot shows the same or almost the same value as the real value which is $\lambda$=10, while the median of the second boxplot is more inaccurate compare to the first one.

- The first boxplot have a lot smaller range (max value - min value) compare to the second.

- The first and third quartile on the first boxplot also have a closer value to the real value compare to the second boxplot.

In conclusion, estimating the value of $\lambda$ using sample mean is more accurate compare to using sample variance.



