---
title: "Homework 5"
author: "Due date: May 3rd, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Written Howework (online assignment on Canvas)
3 attempts are allowed. The latest grade will be kept. Each attempt leads to different question sets. Solutions will be available after deadline. Refer to  [https://en.wikipedia.org/wiki/Significant_figures](https://en.wikipedia.org/wiki/Significant_figures) for significant figure and rounding. 

## Coding Howework (submmite the pdf file to Canvas)

In this homework, we will be playing with the US stock data collected in the past few months. You can download the file ``stock.zip`` from Canvas. The ``.zip`` file have 4 ``.csv`` files, which includes price information of four stocks from January 23 to March 23, 2020:

\begin{enumerate}
\item \verb+VTI+ seeks to track the performance of the CRSP US Total Market Index. See (https://investor.vanguard.com/etf/profile/VTI).
\item \verb+DIS+ : The Walt Disney Company, commonly known as Disney, see (https://thewaltdisneycompany.com/).
\item \verb+AMD+ : Advanced Micro Devices, Inc. is a semiconductor company that developed the Ryzen CPUs and the Radeon graphic cards, see (https://www.amd.com/).
\item \verb+ZM+ : Zoom Video Communications, Inc. is an communications technology company, which provided the software for our online lectures and meetings, see (https://zoom.us/).
\end{enumerate}
We have seen a particularly wild stock market in March. We will apply ANOVA to see if there is a difference in the stock return of the four stocks.

To study the stock return, we will be looking at the \textbf{log return}, defined as 
													$r_t = log(p_t/p_{t-1})$

where $p_t$ is the stock price at day $t$.  We will use the closing price (the \verb+close+ column in the data) as $p_t$. 



Now, answer the following questions.

1. Calculate the log-return for each of the four stocks. Check if we can assume that the log return follows the normal distribution.  Use both the histogram and the Q-Q plot. (20 pt)
```{r q1}
# input your answer here
VTI <- read.csv("VTI.csv")
DIS <- read.csv("DIS.csv")
AMD <- read.csv("AMD.csv")
ZM <- read.csv("ZM.csv")
library(ggplot2)

#Create the log return
VTI$log_return = 0
DIS$log_return = 0
AMD$log_return = 0
ZM$log_return = 0

for (i in 2:length(VTI$Close)) {
  VTI$log_return[i] =  log(VTI$Close[i]/VTI$Close[i-1])
  DIS$log_return[i] =  log(DIS$Close[i]/DIS$Close[i-1])
  AMD$log_return[i] =  log(AMD$Close[i]/AMD$Close[i-1])
  ZM$log_return[i] =  log(ZM$Close[i]/ZM$Close[i-1])
}
head(VTI)
head(DIS)
head(AMD)
head(ZM)

quantile(VTI$log_return)[2]


VTI = data.frame(VTI,
                 group = ifelse(VTI$log_return > quantile(VTI$log_return)[2] - 1.5*IQR(VTI$log_return) &
                                  VTI$log_return < quantile(VTI$log_return)[4] + 1.5*IQR(VTI$log_return), 
                                "main", "outlier"))
DIS = data.frame(DIS,
                 group = ifelse(DIS$log_return > quantile(DIS$log_return)[2] - 1.5*IQR(DIS$log_return) &
                                  DIS$log_return < quantile(DIS$log_return)[4] + 1.5*IQR(DIS$log_return), 
                                "main", "outlier"))
AMD = data.frame(AMD,
                 group = ifelse(AMD$log_return > quantile(AMD$log_return)[2] - 1.5*IQR(AMD$log_return) &
                                  AMD$log_return < quantile(AMD$log_return)[4] + 1.5*IQR(AMD$log_return), 
                                "main", "outlier"))
ZM = data.frame(ZM,
                 group = ifelse(ZM$log_return > quantile(ZM$log_return)[2] - 1.5*IQR(ZM$log_return) &
                                  ZM$log_return < quantile(ZM$log_return)[4] + 1.5*IQR(ZM$log_return), 
                                "main", "outlier"))


#Create the histogram
hist_VTI = ggplot(VTI, aes(x=log_return)) +
  geom_histogram(aes(y=..density..), colour="black", fill="lightblue") +
  geom_density(alpha=.2) + labs(title = "Log Return of VTI", x = "Log Return")
hist_DIS = ggplot(DIS, aes(x=log_return)) +
  geom_histogram(aes(y=..density..), colour="black", fill="lightblue") +
  geom_density(alpha=.2) + labs(title = "Log Return of VTI", x = "Log Return")
hist_AMD = ggplot(AMD, aes(x=log_return)) +
  geom_histogram(aes(y=..density..), colour="black", fill="lightblue") +
  geom_density(alpha=.2) + labs(title = "Log Return of VTI", x = "Log Return")
hist_ZM = ggplot(ZM, aes(x=log_return)) +
  geom_histogram(aes(y=..density..), colour="black", fill="lightblue") +
  geom_density(alpha=.2) + labs(title = "Log Return of VTI", x = "Log Return")

hist_VTI
hist_DIS
hist_AMD
hist_ZM


#Create a Q-Q Plot
qqplot_VTI = ggplot(VTI, aes(sample=log_return, fill=group))+stat_qq()+stat_qq_line()
qqplot_DIS = ggplot(DIS, aes(sample=log_return))+stat_qq()+stat_qq_line()
qqplot_AMD = ggplot(AMD, aes(sample=log_return))+stat_qq()+stat_qq_line()
qqplot_ZM = ggplot(ZM, aes(sample=log_return))+stat_qq()+stat_qq_line()

qqplot_VTI
qqplot_DIS
qqplot_AMD
qqplot_ZM


```

2. Use the Bartlett's test to check if we can assume that the variance from the four population is the same at significance level $\alpha = 0.1$. (10 pt)

```{r q2}
# input your answer here

```

3. Perform the ANOVA test at significance level $\alpha = 0.1$ without using the built-in functions.(10 pt)

```{r q3}
# input your answer here
```
4. Perform the ANOVA test at significance level $\alpha = 0.1$ using the built-in functions. (10 pt)

```{r q4}
# input your answer here
```
5. Use pair-wise $T$-test with Bonferroni adjustment to find the pairs that are significantly different in mean. (10 pt)

```{r q5}
# input your answer here
```
6. State your findings from this study. (5 pt)

Type in your answer here:




